---
title: "R Code for JSSAM Submission"
author: "Qichuan Zhou"
date: "2026-05-10"
output: word_document
---

```{r setup, include=FALSE, tidy=TRUE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE, 
                      autodep=TRUE, cache.comments=FALSE,
                      message=FALSE, warning=FALSE,
                      fig.width=4.5, fig.height=3)
```

# 1, Data Import

```{r}
library(tidyverse)
library(haven)
library(survey)
library(srvyr)
library(kableExtra)
library(flextable)
library(officer)
```

```{r}
data <- read_dta("D:/2025 Winter/SurvMeth 721 Total Survey Error and Data Quality II/Paper Data/ICPSR_2016_Post_Election/ICPSR_37380/DS0001/37380-0001-Data.dta")
```

# 2, Data Cleaning and Preprocessing

## Create age categories

```{r}
data$Q10_18 <- ifelse(data$Q10_18 %in% c(8888, 9999), NA, data$Q10_18) # Converting 8888 and 9999 in the original age variable to NA
data$AGE <- ifelse(!is.na(data$Q10_18), 2017 - data$Q10_18, NA)
data$AGE_CAT <- cut(
         data$AGE,
         breaks = c(-Inf, 24, 34, 49, 64, Inf),
         labels = c("18-24", "25-34", "35-49", "50-64", "65 or higher"), 
         right = TRUE 
) # Creating age categories
```

## Dealing with control variables

```{r}
data$Q10_4A <- ifelse(data$Q10_4A %in% c(88, 99), NA, data$Q10_4A) # marital status
data$Q10_4A[data$Q10_4A == 6] <- 4

data$Q10_901 <- ifelse(data$Q10_901 %in% c(88, 99), NA, data$Q10_901) # employment status
data <- data %>%
  mutate(Q10_901_recode = case_when(
    Q10_901 %in% c(1, 2, 3) ~ 1,  # Currently Employed
    Q10_901 %in% c(4, 5)    ~ 2,  # Currently Unemployed
    Q10_901 == 6            ~ 3,  # Student
    Q10_901 == 7            ~ 4,  # Homemaker
    Q10_901 == 8            ~ 5,  # Retired
    Q10_901 %in% c(9, 10)   ~ 6   # Permanently Disabled and Other
  ))
class(data$Q10_901_recode)

data$S7 <- ifelse(data$S7 == 2, 0, 1) # turning gender from 1/2 to 1/0
data$S9 <- ifelse(data$S9 == 2, 0, 1) # turning if US born from 1/2 to 1/0

# Recode Asian ethnicities
data <- data %>%
  mutate(S10_1_recode = case_when(
    S10_1 %in% c(2, 3, 4, 5, 7, 8, 11) ~ 1,  # East/Southeast Asian
    S10_1 %in% c(1, 6, 10) ~ 2,  # South Asian
    TRUE ~ 3, # Other Asian   
  ))  

```

## Dealing with AA in hiring variables

```{r}
data$AA_hire_ind <- ifelse(!is.na(data$Q7_1A), 1,
                           ifelse(!is.na(data$Q7_1B), 2,
                                  ifelse(!is.na(data$Q7_1C), 3, NA))) # Create a AA hiring question indicator

data$AA_hire_response <- ifelse(!is.na(data$Q7_1A), data$Q7_1A,
                                ifelse(!is.na(data$Q7_1B), data$Q7_1B,
                                       ifelse(!is.na(data$Q7_1C), data$Q7_1C, NA))) # Merge three AA hiring question responses to one

data$AA_hire_response <- ifelse(data$AA_hire_response == 88, 2, # Change 88 to 2 (neutral)
                                ifelse(data$AA_hire_response == 2, 3, # Change 2 to 3 (against)
                                       ifelse(data$AA_hire_response == 99, NA, # Change 99 to NA
                                              data$AA_hire_response)))   # After transformation, 1:For;2:Neutral; 3:Against

```

## Dealing with AA in education variables

```{r}
data$AA_educ_ind <- ifelse(!is.na(data$Q7_3A) | !is.na(data$Q7_3C), 1,
                           ifelse(!is.na(data$Q7_3B) | !is.na(data$Q7_3D), 2, NA)) # Create a AA education question indicator

data$AA_educ_response <- ifelse(!is.na(data$Q7_3A), data$Q7_3A,
                                ifelse(!is.na(data$Q7_3B), data$Q7_3B,
                                       ifelse(!is.na(data$Q7_3C), data$Q7_3C,
                                              ifelse(!is.na(data$Q7_3D), data$Q7_3D, NA)))) # Merge tour AA education question resposnes to one

data$AA_educ_response <- ifelse(data$AA_educ_response %in% c(88, 99), NA, data$AA_educ_response) # Turn 88 and 99 to NA

```

## Two ways of dealing with interviewer race

```{r}
# int_race is a binary variabe with 1 for Asian, 0 for non-Asian
asian_cat <- c(1, 2, 3, 4, 5, 6, 7, 8, 10, 11, 17, 21, 22, 34)
data$int_race <- ifelse(data$Q11_5 %in% asian_cat, 1, 0)

# int_race2 is a nominal variable with 1 for Asian, 2 for White, 3 for Black, 4 for Hispanic, and 5 for Other (Native American and Pacific Islander and Multiracials)
data$int_race2 <- case_when(
  data$Q11_5 %in% c(1,2,3,4,5,6,7,8,10, 11, 17) ~ 1, # Asian
  data$Q11_5 == 31 ~ 2, # White
  data$Q11_5 == 32 ~ 3, # Black
  data$Q11_5 == 33 ~ 4, # Hispanic
  TRUE ~ 5 # Other
)

```

## Dealing with everyday discrimination variables

```{r}
data[, c("Q5_1_B", "Q5_1_E", "Q5_1_D", "Q5_1_G", "Q5_1_H", "Q5_1_J", "Q5_1_K", "Q5_1_C", "Q5_1_I")] <- 
  lapply(data[, c("Q5_1_B", "Q5_1_E", "Q5_1_D", "Q5_1_G", "Q5_1_H", "Q5_1_J", "Q5_1_K", "Q5_1_C", "Q5_1_I")], function(x) {
    ifelse(x %in% c(88, 99), NA, x)
  })  # Convert 88 and 99 in these discrimination variables to NA

data[, c("Q5_1_B", "Q5_1_E", "Q5_1_D", "Q5_1_G", "Q5_1_H", "Q5_1_J", "Q5_1_K", "Q5_1_C", "Q5_1_I")] <- 
  lapply(data[, c("Q5_1_B", "Q5_1_E", "Q5_1_D", "Q5_1_G", "Q5_1_H", "Q5_1_J", "Q5_1_K", "Q5_1_C", "Q5_1_I")], function(x) {
    ifelse(x == 2, 0, x)
  }) # Convert No response from 2 to 0

```

## Dealing with Intergroup Contact variables

```{r}
data[, c("Q6_1_A", "Q6_1_B", "Q6_1_C")] <- 
  lapply(data[, c("Q6_1_A", "Q6_1_B", "Q6_1_C")], function(x) {
    ifelse(x %in% c(88, 99), NA, x)
  }) # Convert 88 and 99 in these variables to NA

```

## Select all the necessary variables related to this research

```{r}
selected_vars <- c(
  # Everyday Discrimination variables
  "Q5_1_B", "Q5_1_C", "Q5_1_D", "Q5_1_E", "Q5_1_G", "Q5_1_H", "Q5_1_I", "Q5_1_J", "Q5_1_K",
  
  # Affirmative Action responses
  "AA_hire_response", "AA_educ_response",
  
  # Interviewer Race (Binary and Dummy-coded)
  "int_race", "int_race2",
  
  # Intergroup Contact (Ordinal)
  "Q6_1_A", "Q6_1_B", "Q6_1_C",
  
  # Control Variables
  "AGE_CAT", "Q10_4A", "Q10_901_recode",
  "S7", "S8", "S10_1_recode", "FORBORN",
  
  # Question Framing Indicators (Dummy-coded)
  "AA_hire_ind", "AA_educ_ind",
  
  # Respondent Race
  "RACE", 
  
  # Weight
  "NWEIGHTNATIVITY",
  
  #STRATA Indicator
  "ETHNICALPHA"
)

data2 <- data[, selected_vars]


# Setting the reference category
data2$AA_hire_response <- as.factor(data2$AA_hire_response)
data2$AA_hire_response <- relevel(data2$AA_hire_response, ref = "3")

data2$AA_educ_response <- as.factor(data2$AA_educ_response)
data2$AA_educ_response <- relevel(data2$AA_educ_response, ref = "5")

# Define survey design
library(survey)
naas_full_design <- svydesign(
  ids = ~1, 
  strata = ~ETHNICALPHA,       
  weights = ~NWEIGHTNATIVITY,  
  data = data2
)

# Subset the Asian Americans from the full design 
asian_design <- subset(naas_full_design, RACE == 1)

# Filter out the dataset with only Asian American respondents
data3 <- data2 %>% filter(RACE == 1)

```

# 3, Descriptive Analysis

```{r}
demographic_vars <- c("AGE_CAT", "Q10_4A", "Q10_901_recode", "S7", "S8", "FORBORN", "S10_1_recode")

for(var in demographic_vars) {
  data3[[var]] <- as.factor(data3[[var]])
  asian_design$variables[[var]] <- as.factor(asian_design$variables[[var]])
}

unweighted_proportions <- lapply(demographic_vars, function(var) {
  prop.table(table(data3[[var]])) %>% round(3) 
})

library(srvyr)

weighted_proportions <- lapply(demographic_vars, function(var) {
  asian_design %>%
    srvyr::as_survey() %>% # Converts the survey object 
    group_by(across(all_of(var))) %>% 
    summarize(
      Weighted_Proportion = survey_mean(na.rm = TRUE)
    ) %>%
    mutate(across(c(Weighted_Proportion, Weighted_Proportion_se), round, 3))
})

weighted_proportions[[7]]
```

# 4, Bivariate Analysis

```{r}
discrimination_vars <- c("Q5_1_B", "Q5_1_C", "Q5_1_D", "Q5_1_E", "Q5_1_G", "Q5_1_H", "Q5_1_I", "Q5_1_J", "Q5_1_K")
aa_vars             <- c("AA_hire_response", "AA_educ_response")

srvyr_design <- as_survey(asian_design)

bivariate_discrimination <- lapply(discrimination_vars, function(var) {
  srvyr_design %>%
    # Group by interviewer race and the specific discrimination variable
    group_by(int_race, across(all_of(var))) %>%
    summarize(
      Weighted_Prop = survey_mean(na.rm = TRUE)
    ) %>%
    mutate(
      Variable = var,
      across(c(Weighted_Prop, Weighted_Prop_se), round, 3)
    )
})

bivariate_discrimination[[9]]
```

```{r}
bivariate_aa <- lapply(aa_vars, function(var) {
  srvyr_design %>%
    # Group by interviewer race and the specific AA response variable
    group_by(int_race, across(all_of(var))) %>%
    summarize(
      Weighted_Prop = survey_mean(na.rm = TRUE)
    ) %>%
    mutate(
      Variable = var,
      across(c(Weighted_Prop, Weighted_Prop_se), round, 3)
    )
})

bivariate_aa[[2]]
```

```{r}
# Conduct Rao-Scott Chi-Square tests 
rs_discrimination_results <- lapply(discrimination_vars, function(var) {
  # Create the formula dynamically (e.g., ~Q5_1_B + int_race)
  form <- as.formula(paste0("~", var, " + int_race"))
  
  # Run the Rao-Scott Chi-Square test (statistic = "F" is the standard Rao-Scott second-order correction)
  test_output <- svychisq(form, design = asian_design, statistic = "F")
  
  # Extract relevant statistics into a clean dataframe
  data.frame(
    Variable = var,
    F_Statistic = round(test_output$statistic, 3),
    df_num = test_output$parameter[1],
    df_den = round(test_output$parameter[2], 1),
    p_value = round(test_output$p.value, 4)
  )
})

discrimination_chisq_table <- do.call(rbind, rs_discrimination_results)

rs_aa_results <- lapply(aa_vars, function(var) {
  form <- as.formula(paste0("~", var, " + int_race"))
  test_output <- svychisq(form, design = asian_design, statistic = "F")
  
  data.frame(
    Variable = var,
    F_Statistic = round(test_output$statistic, 3),
    df_num = test_output$parameter[1],
    df_den = round(test_output$parameter[2], 1),
    p_value = round(test_output$p.value, 4)
  )
})

aa_chisq_table <- do.call(rbind, rs_aa_results)
```

# 5, Explore ROI Effects (Discrimination Experiences)

```{r}
data2 <- data2 %>%
  mutate(
    AGE_CAT        = as.factor(AGE_CAT),
    Q10_4A         = as.factor(Q10_4A),         # Marital Status
    Q10_901_recode = as.factor(Q10_901_recode), # Employment Status
    S7             = as.factor(S7),             # Gender
    S8             = as.factor(S8),             # Education level
    S10_1_recode   = as.factor(S10_1_recode),   # 2-Category Ethnicity Cluster
    FORBORN        = as.factor(FORBORN),        # Nativity
    int_race       = as.factor(int_race),
    int_race2      = as.factor(int_race2)
  )

data2$FORBORN      <- relevel(data2$FORBORN, ref = "0")      # Baseline: Native-born
data2$S10_1_recode <- relevel(data2$S10_1_recode, ref = "1")  # Baseline: East/Southeast Asian

naas_full_design <- svydesign(
  ids = ~1, 
  strata = ~ETHNICALPHA,       
  weights = ~NWEIGHTNATIVITY,  
  data = data2
)

asian_design <- subset(naas_full_design, RACE == 1)
```

```{r}
model1 <- svyglm(Q5_1_B ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model2 <- svyglm(Q5_1_C ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model3 <- svyglm(Q5_1_D ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model4 <- svyglm(Q5_1_E ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model5 <- svyglm(Q5_1_G ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model6 <- svyglm(Q5_1_H ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model7 <- svyglm(Q5_1_I ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model8 <- svyglm(Q5_1_J ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)
model9 <- svyglm(Q5_1_K ~ int_race + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN, family = quasibinomial(), design = asian_design)

summary(model9)

length(model9$residuals)
```

```{r}
### Convert the raw coefficients to odds ratios and combine nine model outputs into one table
# Function to extract odds ratios and significance stars
extract_or <- function(model) {
  coef_est <- exp(coef(model)) # Exponentiate coefficients to get odds ratios
  p_values <- summary(model)$coef[, 4] # Extract p-values
  
  # Add significance stars
  significance <- ifelse(p_values < 0.001, "***", 
                         ifelse(p_values < 0.01, "**", 
                                ifelse(p_values < 0.05, "*", "")))
  
  # Combine odds ratio with significance stars
  formatted_or <- sprintf("%.3f%s", coef_est, significance)
  return(formatted_or)
}

# Function to calculate McFadden's R²
calculate_pseudo_r2 <- function(model) {
  null_model <- svyglm(formula = update(formula(model), . ~ 1), 
                       design = model$survey.design, 
                       family = quasibinomial())
  return(round(1 - (logLik(model) / logLik(null_model)), 3))
}

# Function to calculate effective sample size
calculate_ess <- function(model) {
  return(summary(model)$df.residual + 1)
}

models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9)

# Extract odds ratios for all models
odds_ratios_list <- lapply(models, extract_or)
odds_ratios_df <- do.call(cbind, odds_ratios_list)

# Get variable names (row names from the first model)
variable_names <- names(coef(models[[1]]))

# Create a dataframe for odds ratios
results_df <- data.frame(Variable = variable_names, odds_ratios_df)
colnames(results_df) <- c("Variable", paste0("Model ", 1:9)) 

# Calculate McFadden’s R² and effective sample size
pseudo_r2_values <- sapply(models, calculate_pseudo_r2)
effective_sample_sizes <- sapply(models, calculate_ess)

pseudo_r2_values
effective_sample_sizes

# Create a dataframe for McFadden’s R² and ESS
model_fit_df <- data.frame(
  Variable = c("Effective Sample Size", "McFadden’s R²"),
  rbind(effective_sample_sizes, pseudo_r2_values)
)

colnames(model_fit_df) <- c("Variable", paste0("Model ", 1:9))

# Combine odds ratio table with model fit statistics
model_fit_df <- model_fit_df %>% mutate(across(where(is.numeric), as.character)) # Convert model fit data to character
final_table <- bind_rows(results_df, model_fit_df)

# Rename the variable names in the table
final_table <- final_table %>%
  mutate(Variable = recode(Variable, 
    "int_race" = "Interviewer Race (Asian)",
    "AGE_CAT2" = "Age: 25-34",
    "AGE_CAT3" = "Age: 35-49",
    "AGE_CAT4" = "Age: 50-64",
    "AGE_CAT5" = "Age: 65+",
    "Q10_4A2" = "Marital Status: Widowed",
    "Q10_4A3" = "Marital Status: Divorced",
    "Q10_4A4" = "Marital Status: Separated",
    "Q10_4A5" = "Marital Status: Never married",
    "Q10_901_recode2" = "Employment: Currently unemployed",
    "Q10_901_recode3" = "Employment: Student",
    "Q10_901_recode4" = "Employment: Homemaker",
    "Q10_901_recode5" = "Employment: Retired",
    "Q10_901_recode6" = "Employment: Permanently disabled",
    "S71" = "Gender: Male",
    "S82" = "Education: Some Schooling",
    "S83" = "Education: High School Graduate",
    "S84" = "Education: Some College",
    "S85" = "Education: Bachelor's Degree",
    "S86" = "Education: Graduate Degree",
    "S10_1_recode2" = "Ethnicity: South Asian",
    "FORBORN1" = "Nativity: Foreign-born"
  ))
 final_table <- final_table %>%
  rename(
    "Received poorer service" = "Model 1",
    "People assume you don't speak English" = "Model 2",
    "People act afraid of you" = "Model 3",
    "People assume you are dishonest" = "Model 4",
    "Called names or insulted" = "Model 5",
    "Threatened or harassed" = "Model 6",
    "Name mispronounced" = "Model 7",
    "Assumed good at math/science" = "Model 8",
    "Assumed not creative" = "Model 9"
  )
 

```

# 6, Exploring ROI Effects (Affirmative Action)

```{r}
library(svyVGAM)

model10 <- svy_vglm(AA_educ_response ~ int_race2 + Q6_1_A + Q6_1_B + Q6_1_C + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN + AA_educ_ind, family = multinomial(), design = asian_design)

summary(model10)

model11 <- svy_vglm(AA_hire_response ~ int_race2 + Q6_1_A + Q6_1_B + Q6_1_C + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN + AA_hire_ind, family = multinomial(), design = asian_design)

summary(model11)

nrow(model10$X)
```

```{r}
### Convert the raw coefficients to odds ratios and combine nine model outputs into one table
raw_results <- coef(model11)

# Compute odds ratios
odds_ratios <- exp(raw_results)
odds_ratios_df <- as.data.frame(odds_ratios)
odds_ratios_df <- odds_ratios_df %>% 
  mutate(across(1:1, ~ round(., 3)))
odds_ratios_df_cleaned <- odds_ratios_df %>% 
  rownames_to_column(var = "Variable") %>%  # If the row names contain variable information
  separate(Variable, into = c("Variable", "Category"), sep = ":", fill = "right") %>%
  pivot_wider(names_from = Category, values_from = odds_ratios)
```

# 7, Test the moderation effect of Q6_1_C

```{r}
model12 <- svy_vglm(AA_educ_response ~ int_race2*Q6_1_C + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN + AA_educ_ind, family = multinomial(), design = asian_design)

summary(model12)

model13 <- svy_vglm(AA_hire_response ~ int_race2*Q6_1_C + AGE_CAT + Q10_4A + Q10_901_recode + S7 + S8 + S10_1_recode + FORBORN + AA_hire_ind, family = multinomial(), design = asian_design)

summary(model13)

```

```{r}
raw_results <- coef(model13)
raw_results <- as.data.frame(raw_results)
raw_results <- raw_results %>% 
  mutate(across(1:1, ~ round(., 3)))
raw_results_cleaned <- raw_results %>% 
  rownames_to_column(var = "Variable") %>%  # If the row names contain variable information
  separate(Variable, into = c("Variable", "Category"), sep = ":", fill = "right") %>%
  pivot_wider(names_from = Category, values_from = raw_results)
  
```



























































































































